On the Minimum Core Mass for Giant Planet Formation through Kelvin-Helmholtz Contraction

### 2013-02-22 tex/draft/draft2.tex
updated plots

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/TdPd_effect.pdf}
%\vspace{-0.5in}
\caption{Disk temperature effect on growth time. Gas accretion is faster for lower temperatures.}
\end{figure}

@@

>>>>

\begin{figure*}[tb]
\centering
\includegraphics[width=1.\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/TdPd_effect.pdf}
%\vspace{-0.5in}
\caption{Disk temperature effect on growth time. Gas accretion is faster for lower temperatures.}
\end{figure*}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/cooling_a10_Mc5_rcb.pdf}
%\vspace{-0.5in}
\caption{}
\end{figure}
